---
title: "Evaluations of positive and negative stimuli using the Affective Misattribution Procedure (AMP) and self-reports"
subtitle: "Data processing"
author: "Template: Ian Hussey; content: [Student name]"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

# TODO

- Add data processing
- Combine data frames
- Save to disk

```{r, include=FALSE}

knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE)

```

# Dependencies

```{r}

library(tidyverse)
library(janitor) # for clean_names()
library(stringr)

```

# Get data

```{r}

# demographics
data_demographics_raw <- read_csv("../../../data/AMP study/raw/data_demographics_raw.csv")

data_demographics_raw_messy <- read_csv("../../../data/AMP study/raw/data_demographics_raw_messy.csv", skip = 2)
#data_demographics_raw_messy <- read_csv("../../../data/AMP study/raw/data_demographics_raw_messy.csv")
#how manyy rows should I skip? 2

# self report measure
data_selfreport_raw <- read_csv("../../../data/AMP study/raw/data_selfreport_raw.csv")

# affect attribution procedure
data_amp_raw <- read_csv("../../../data/AMP study/raw/data_amp_raw.csv") 

```


# Slice

```{r}

```


```{r}
dat_gender <- data_demographics_raw_messy %>% 
  rename(response = `!! Key response`)
```


# Demographics

TODO extract age and gender data into wide format

# Q1: data_demographics_raw_messy.csv contains (fake) sensitive data that legally cannot be made open. If it was real data, it should never be put on a public github repo where others can access it. What function would you use to drop these rows from the dataset?
 - to drop these columns age and gender I'd use select (), either by selecting the ones I want
 to keep or the ones I want to remove by -
 
# Q2: data_demographics_raw.csv contains more columns than needed. Which ones are important to extract, and what function would you use to do this? 
- I'd  use the select() function as well

```{r}

data_demographics_raw_messy <- data_demographics_raw_messy |>
  clean_names() |> 
  filter(!trial_code %in% c("prolific ID", "psychiatric diagnosis"))

# select relevant column
dat_gender <- data_demographics_raw %>% 
  clean_names() |> 
  select(subject, date, time, trialcode, response)

# gender
dat_gender <- dat_gender |> 
  filter(trialcode == "gender") |> 
  rename(gender = response) |> 
  mutate(gender = tolower(gender),
         gender = stringr::str_remove_all(gender,
                                          regex("\\W+")),
         gender = case_when( gender == "female" ~ gender,
         gender == "male" ~ gender,
         gender == "nonbinary" ~ gender,
         gender == "woman" ~ "female",
         gender == "man" ~ "male",
         TRUE ~ "other/error/missing")) |> 
  select(-trialcode)

# count
dat_gender |> 
  count(gender)

# age variable
dat_age <- data_demographics_raw_messy |> 
  clean_names()

dat_age <- dat_age |> 
  select(subject, date, time, trial_code, key_response) |> 
  filter(trial_code == "age") |> 
  rename(age = trial_code) |> 
  mutate(age = as.numeric(age),
         age = ifelse(is.na(age), "other/error/missing", age))

#combine gender and age data frame
dat_age_gender <- 
  full_join(dat_age,data_demographics)


## My way

# names
data_demographics |> 
  distinct(trialcode) |> 
  pull()

# not names and not measurements, id_cols
data_demographics |> 
  select(-trialcode, -response) |> 
  distinct()

# identify duplicates
data_demographics |> 
  group_by(subject, trialcode) |> 
  summarize(n = n(), .groups = "drop") |> 
  filter(n > 1)

duplicates <- data_demographics |> 
  filter(subject == "246532124")

data_demographics <- data_demographics |> 
  slice(-c(7, 8))

# pivot wider
data_demo_wide <- data_demographics |> 
  pivot_wider(
    names_from = trialcode,
    values_from = response
  )
View(data_demo_wide)

# create new column with mutate()
data_demo_wide$age <- as.numeric(data_demo_wide$age )
data_demo_wide <- data_demo_wide |> 
  mutate(months = age *12)


```




# Exclusions / data quality?

```{r}


```

# Self-reports

TODO extract self-reported evaluations and convert to a sum score

```{r}



```

# Affect Misattribution Procedure

TODO extract evaluations on the AMP test blocks and convert to an overall bias score

```{r}



```

# Combine

TODO combine demographics, self-reports and AMP into a single data frame in wide format, i.e., the processed data

```{r}



```

# Write to disk

TODO write the processed data to disk

```{r}



```

# Session info

```{r}

sessionInfo()

```


