---
title: "Evaluations of positive and negative stimuli using the Affective Misattribution Procedure (AMP) and self-reports"
subtitle: "Analysis"
author: "Template: Ian Hussey; content: [Student name]"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

# TODO

- Demographics summary
- Analyses
- ...?

```{r, include=FALSE}

# set knit options
knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE)

# disable scientific notation
options(scipen = 999) 

```

# Dependencies

```{r}

library(tidyverse)

```

# Get data

```{r}
# keep all the data processing in the data processing and 
# all the analysis in the analysis, whenever I think i need to go back to processing
data_processed <- read_csv("../../../data/AMP study/processed/data_processed.csv")

```

# Sample descriptives
# create tables with mean age sd age, count of genders, and % of sample of each gender.

```{r}
data_processed |>
  count(age)

#dat_descriptives <- data_processed |>
#  mutate(age = as.numeric(age)) |> 
#  summarise(mean_age = mean(age), na.rm = TRUE,
#            sd_age = sd(age)) |> 
#  mutate(mean_age =round(mean_age, 2),
#         sd_age = round(sd_age, 2))

library(knitr)
library(kableExtra)
       
dat_descriptives <- data_processed |>
  mutate(age = as.numeric(age)) |> 
  summarise(mean_age = mean(age, na.rm = TRUE),
            sd_age = sd(age, na.rm = TRUE)) |> 
  mutate(mean_age = round(mean_age, 2),
          sd_age = round(sd_age, 2)) |> 
  kbl(format = "html") |> 
  kable_classic(full_width = FALSE)

dat_descriptives

#Alternative
# mutate_all(.funs = janitor::round_half_up, digits=2) 
  
#R rounds differently: bankers rounding, does not work the way we think
#vec <- c(0.5, 1.5, 2.5, 3.5, 4.5)

#round(vec, 0)

#to round as we know
#janitor::round_half_up(vec, 0)


```



# a table of overall sample size

```{r}

sample_size <- data_processed |>
  summarise(sample_size = n()) |> 
  kbl(format = "html") |> 
  kable_classic(full_width = FALSE)

sample_size


```


#A table with both counts and percentages of each gender in the sample.

```{r}

#absolut and relative numbers of gender

dat_gender <- data_processed |>
  group_by(gender) |> 
  summarise(gender_n = n(), 
            gender_p = round((n()/102*100), 2)) |> 
  kable(format = "html") |> 
  kable_classic(full_width = FALSE)

dat_gender



```


# A table with the mean and standard deviation of mean_evaluation, a) for the overall sample, and b) for each gender category.

```{r}


dat_descriptives <- data_processed |>
  mutate(age = as.numeric(age)) |> 
  group_by(gender) |> 
  summarise(mean_age = mean(age, na.rm = TRUE),
            sd_age = sd(age, na.rm = TRUE)) |> 
  mutate(mean_age = round(mean_age, 2),
          sd_age = round(sd_age, 2)) |> 
  kbl(format = "html") |> 
  kable_classic(full_width = FALSE)

dat_descriptives

```


# Analyses

## Self-reported evalautions

```{r}



```

## Evaluations on the Affect Misattribution Procedure

```{r}



```

# Session info

```{r}

sessionInfo()

```



